Energy and the CES production function

### 2015-09-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Historical plot now same style as alpha graph.

historicalPlot(
  histDataForGraph, 
  mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
  facet_formula = flavor ~ Country, 
  line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
xlab("") + 
scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
ylab("Indexed (1960=1)")
@

>>>>

ggplot(histDataForGraph) + 
  geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +
  facet_grid(flavor ~ Country) + 
  scale_color_manual(name = "", values=c("black", "black", "black", "gray70")) +
  scale_linetype_manual(name="", values=c(1,2,3,1)) + 
  scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
  xlab("") + 
  ylab("Indexed (1960=1)") +
  xy_theme()
@
